### 2014-10-15 RelatedWork.tex
related work

%There has been a lot of work in providing frameworks for axiomatic
%specifications of memory models \cite{alglave2012formal,alglave2014herding}
%and in providing axiomatic memory model specifications for real systems
%through analyis of empirically observed behavior of certain ``litmus tests''
%\cite{mador2012axiomatic,sarkar2012synchronising}. There has also been some
%work in providing operational semantics that describes the observed behavior of
%real hardware \cite{sarkar2011understanding}. Finally, there has been work
%formally relating the axiomatic specification of TSO to operational semantics
%of real x86 and Sparc machines \cite{x86tsocacm10}.
%
%The plethora of work in the area of memory models indeed suggests that this is
%a complex problem, exacerbated by the hardware architect's desire to increase
%hardware performance at the cost of complicating the memory models further. There
%are two aspects where our work can help in tackling this complex problem: (1) we
%are proposing a modular approach for verifying systems in which the components,
%namely the processors and the memory, can be verified against the memory model
%contract independent of each other, and (2) we are also proposing a design
%in which a system obeying sequential consistency is made into a high
%performance machine through the use of speculative loads followed by
%verification. The only downside is waiting for store acknowledgements, but this
%wait does not preclude the machine from performing further computations for
%future instructions without actually committing them. We are hoping to develop
%both these ideas -- of extending our proof approach for more complex memory
%models and designing real hardware which is sequentially consistent but has
%high performance.
%
%
%BELOW IS UNEDITTED FROM OLD PAPER

>>>>

\xxx{TODO: Correct This}

There has been a lot of work in providing frameworks for axiomatic
specifications of memory models based on empirically observed behavior of
certain ``litmus
tests''\cite{alglave2012formal,alglave2014herding,Alglave:FMSD,Alglave:2010,Alglave11,Alglave:TACAS}.
There has been some work in providing operational and axiomatic semantics that
describes the observed behavior (based on certain ``litmus tests'' of real
hardware
\cite{mador2012axiomatic,sarkar2011understanding,sarkar2012synchronising}.
Finally, there has been work formally relating the axiomatic specification of
TSO to operational semantics \cite{x86tsocacm10}.

%There has been a lot of work in providing frameworks for axiomatic
%specifications of memory models \cite{alglave2012formal,alglave2014herding}
%and in providing axiomatic memory model specifications for real systems
%through analysis of empirically observed behavior of certain ``litmus tests''
%\cite{mador2012axiomatic,sarkar2012synchronising}. There has also been some
%work in providing operational semantics that describes the observed behavior of
%real hardware \cite{sarkar2011understanding}. Finally, there has been work
%formally relating the axiomatic specification of TSO to operational semantics\cite{x86tsocacm10}.

%The plethora of work in the area of memory models indeed suggests that this is
%a complex problem, exacerbated by the hardware architect's desire to increase
%hardware performance at the cost of complicating the memory models further. There
%are two aspects where our work can help in tackling this complex problem: (1) we
%are proposing a modular approach for verifying systems in which the components,
%namely the processors and the memory, can be verified against the memory model
%contract independent of each other, and (2) we are also proposing a design
%in which a system obeying sequential consistency is made into a high
%performance machine through the use of speculative loads followed by
%verification. The only downside is waiting for store acknowledgements, but this
%wait does not preclude the machine from performing further computations for
%future instructions without actually committing them. We are hoping to develop
%both these ideas -- of extending our proof approach for more complex memory
%models and designing real hardware which is sequentially consistent but has
%high performance.
%

%BELOW IS UNEDITTED FROM OLD PAPER
